Effects of resonant and random excitations on the proton beam in the Large Hadron Collider, with applications to the design of pulsed hollow electron lenses for active halo control

### 2018-03-25 resex.tex
Added aps class option, removed babel, replaced rms with standard deviation in introduction.

\documentclass[
prstab
,reprint
%,draft
%,preprint,tightenlines
,linenumbers
,longbibliography
,preprintnumbers
%,showpacs
,showkeys
,amsfonts,amssymb,amsmath
,floatfix
]{revtex4-1}

\usepackage[american]{babel}
\usepackage{bm}
\usepackage{dcolumn}
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage[colorlinks=true, allcolors=NavyBlue]{hyperref}

@@

Considering past, current and future high energy colliders, each new
machine has represented a considerable leap in stored beam energy
(Table~\ref{tab:stored_energy}). Furthermore, recent measurements at
the LHC show that the tails of the transverse beam distribution are
overpopulated compared to a Gaussian distribution. This results in a
considerable amount of energy being stored in the beam tails. In
particular, in the case of the LHC, about 5\% of the beam population
is stored in the tails (i.e., above 3.5$\sigma$, where $\sigma$ is the
Gaussian root-mean-square beam size), compared to 0.22\% in an ideal
Gaussian distribution, leading to 19~MJ of stored energy for nominal
LHC parameters and 34~MJ in the case of
HL-LHC~\cite{helreview_valentino}. This leads to the conclusion that a
mechanism is needed to deplete the beam tails in a controlled
manner. Further information on the needs for halo control in LHC can
be found in Ref.~\cite{helreview}.

>>>>

\documentclass[aps
,prstab
,reprint
%,draft
%,preprint,tightenlines
,linenumbers
,longbibliography
,preprintnumbers
%,showpacs
,showkeys
,amsfonts,amssymb,amsmath
,floatfix
]{revtex4-1}

\usepackage{bm}
\usepackage{dcolumn}
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage[colorlinks=true, allcolors=NavyBlue]{hyperref}

@@

Considering past, current and future high energy colliders, each new
machine has represented a considerable leap in stored beam energy
(Table~\ref{tab:stored_energy}). Furthermore, recent measurements at
the LHC show that the tails of the transverse beam distribution are
overpopulated compared to a Gaussian distribution. This results in a
considerable amount of energy being stored in the beam tails. In
particular, in the case of the LHC, about 5\% of the beam population
is stored in the tails (i.e., above 3.5$\sigma$, where $\sigma$ is the
standard deviation of the Gaussian beam core), compared to 0.22\% in
an ideal Gaussian distribution, leading to 19~MJ of stored energy for
nominal LHC parameters and 34~MJ in the case of
HL-LHC~\cite{helreview_valentino}. This leads to the conclusion that a
mechanism is needed to deplete the beam tails in a controlled
manner. Further information on the needs for halo control in LHC can
be found in Ref.~\cite{helreview}.
